---
title: "Reproducing LOF scores"
output: html_document
---

```{r, echo=FALSE}
load("../Desktop/kddcup.data_10_percent_corrected.RData")
```

- There are 42 features (including a feature for labels).
- LOF scores are computed on the numeric features only (34 of them) with `k = 3`.
- There are `494021` individuals in the dataset, `352542` of which are duplicated entries (about 71.4% are duplicates).
    - LOF computation results in an overflow error because of these duplicates (a lot of `NaN`s produced) so these duplicates are dropped from the dataset.
    - About 97.3% of the duplicates (342982) are attacks so we may drop them (safely?) and leave one duplicate as an attack.

```{r, eval=FALSE}
library(DMwR)
dat2 = subset(dat, select=-c(2,3,4,7,12,20,21,22,42))
dat3 = dat2[!duplicated(dat2), ]
outlier.scores = lofactor(dat3, k=3)

sum(outlier.scores > 1)
dat4 = dat3
dat4$attack_type = dat[!duplicated(dat2), 42]
```

```{r, echo=-1}
load("../Desktop/outlier.scores.RData")
## Detection rate:
sum(outlier.scores > 1.1) / sum(dat4$attack_type != "normal.")

```







